---
title: "Individual2 Lab 3"
author: "Meredith Tucker mltucker2001"
date: "2/19/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(ggplot2)
```

```{r}
dat <- readxl::read_xls('C:/Users/mltuc/Documents/DS 202/ds202_lab3/GSS.xls')
predictors <- c('Year', 'Javsatif', 'Happy', 'Religion', 'Education', 'Addiction', 'Cityproblems', 'Space', 'Party', 'Race', 'Sex', 'Schoolyear', 'Age', 'Children', 'Status', 'ID', 'Ballot')
names(dat) <- predictors
dat$Year <- as.factor(dat$Year)
```


1. How does the happiness of a respondent relate to the marriage status?

```{r}

ggplot(dat, aes(x=Happy, fill=Status)) + geom_bar()

```

As the happyness level increases as appears on the chart, the higher the number of marriages.

2. Does the sex of the respondent affect the relationship you found in Q1?
```{r}
ggplot(dat, aes(x=Happy, fill=Status)) +geom_bar() +facet_wrap(~Sex)
```

The level of women appear to be happier then the number of men. However there is a happier number of widowed women over the the number of widowed men.

3. How does the happiness of a respondent relate to the political party affiliation?

```{r}
ggplot(dat, aes(x=Happy, fill=Party)) + geom_bar()

```
I don't believe that the party plays a large role on the happiness level. Most people say that they are happy.



