---
title: "team"
author: "Mike Zaino"
date: "2/22/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(ggplot2)
```

```{r}
dat <- readxl::read_xls('/Users/TheemikezanilyMac/Documents/School/DS 202/ds202_lab3/GSS.xls')
predictors <- c("Year", "Jobsatif", "Happy", "Religion", "Education", "Addiction", "Cityproblems", "Space", "Party", "Race", "Sex", "Schoolyear", "Age", "Children", "Status", "ID", "Ballot")
names(dat) <- predictors
dat$Year <- as.factor(dat$Year)
```

1. Does your religion and political party association have any correlation?
```{r}
ggplot(dat, aes(x=Party, fill=Religion))+geom_bar()+coord_flip()+theme_bw()+facet_wrap(~Religion, scales="free_x")
```

Looking at the graph, we can see that Protestant, Jewish, and Islam all favor democratic. This makes sense as their religion favors more democratic ideals. Catholic has more of an even spread across all the ideals. Lastly, the dont know category has a lot of independent people. This is because they do not favor any ideals and are in the middle of both republican and democrat.

2. Does your education level and party dictate views on the national education system?

```{r}
table(dat$Schoolyear)
dat$Schoolyear <- factor(dat$Schoolyear, levels = c('0','1','2','3','4','5','6','7','8','9','10','11','12','13','14','15','16','17','18','19','20', 'Dont know', 'No answer'))
ggplot(dat, aes(x=Schoolyear, fill=Party))+geom_bar()+theme_bw()+coord_flip()+facet_wrap(~Education, scales="free_x")
```

From the graph, we can see that most people only graduated high school at grade 12. Form those people, we can see that if you are republican, you favor that education is too much and would like it to change. On the other hand, if you finished grade 12 and are democrat, you favor the education  system is about right and there does not need to be a change.





